Quantum-Classical Phase Transition for Exciton-Polariton Josephson Junctions

### 2017-01-13 writing/phase_transition/phase_transition.tex
Two figures combined in one

Consider the imaginary-time action
%
\begin{equation}
S(T) = \oint (\tfrac{1}{2} \dot{z}^2 + s^2 V_0(z)) d \tau
\label{eq:thermon_action_1}
\end{equation}
%
Periodic, with $\tau_p = \hbar / k_B T$, solutions of (\ref{eq:thermon}) satisfy the relation
%
\begin{equation}
\tfrac{1}{2} \dot{z}^2 = s^2 V_0(z) - E(\tau_p),
\label{eq:total_energy}
\end{equation}
%
where $\tau_p$ is a thermon period corresponding to the energy level $E(\tau_p)$;
%
\begin{equation}
\tau_p(E) = \sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz,
\label{eq:thermon_period}
\end{equation}
%
here $z_{1,2}(E)$ -- turning points.
Using (\ref{eq:total_energy}) rewrite (\ref{eq:thermon_action_1}) in a form 
%
\begin{equation}
S(T) = 2\sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz + E \tau_p (E).
\label{eq:thermon_action_2}
\end{equation}
%
We draw dependence $S(T)$ and $\tau_p(E)$ for the cases of the 1st and 2nd order phase transition.
For the sake of convenience we suppose that $V_0(z) = 0$ at minima surrounding the barrier.
So, $E = 0$ corrensponds to the separatrices instanton solution (May be we should make corresponding transformation earlier).
%
\begin{figure}[ht]
\center{\includegraphics[width=\linewidth]{pic/action_period_1st_order_transition.eps}}
\caption{1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$}
\end{figure}
%
\begin{figure}[ht]
\center{\includegraphics[width=\linewidth]{pic/action_period_2nd_order_transition.eps}}
\caption{2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$}
\end{figure}
%

>>>>

Consider the imaginary-time action
%
\begin{equation}
S(T) = \oint (\tfrac{1}{2} \dot{z}^2 + s^2 V_0(z)) d \tau
\label{eq:thermon_action_1}
\end{equation}
%
Periodic, with $\tau_p = \hbar / k_B T$, solutions of (\ref{eq:thermon}) satisfy the relation
%
\begin{equation}
\tfrac{1}{2} \dot{z}^2 = s^2 V_0(z) - E(\tau_p),
\label{eq:total_energy}
\end{equation}
%
where $\tau_p$ is a thermon period corresponding to the energy level $E(\tau_p)$;
%
\begin{equation}
\tau_p(E) = \sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz,
\label{eq:thermon_period}
\end{equation}
%
here $z_{1,2}(E)$ -- turning points.
Using (\ref{eq:total_energy}) rewrite (\ref{eq:thermon_action_1}) in a form 
%
\begin{equation}
S(T) = 2\sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz + E \tau_p (E).
\label{eq:thermon_action_2}
\end{equation}
%
We draw dependence $S(T)$ and $\tau_p(E)$ for the cases of the 1st and 2nd order phase transition.
For the sake of convenience we suppose that $V_0(z) = 0$ at minima surrounding the barrier.
So, $E = 0$ corrensponds to the separatrices instanton solution (May be we should make corresponding transformation earlier).
%
\begin{figure}[ht]
\center{\includegraphics[width=\linewidth]{pic/action_period_combined.eps}}
\caption{(a) 1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$; (b) 2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$}
\end{figure}
%
